---
title: "A logbook for RoLE Forest"
output: html_notebook
---

```{r}
plot(cars)
```

Plotting relative abundance of orders and families for insects triaged so far (Oct 2022):

```{r}

insects <- read.csv('data/RoLE_Insects_Triage_oct2022.csv')

ara.abundance <- insects %>% filter(Island == 'ARA') %>% group_by(Família) %>%
  summarise(Order = unique(Ordem), N = sum(Nº.de.especimes)) %>% arrange(desc(N))

uba.abundance <- insects %>% filter(Island == 'UBA') %>% group_by(Família) %>%
  summarise(Order = unique(Ordem), N = sum(Nº.de.especimes)) %>% arrange(desc(N))

data <- rbind(ara.abundance,uba.abundance)

plotdata <- data.frame(data, island = c(rep('Araripe',nrow(ara.abundance)),
                                        rep('Ubajara',nrow(uba.abundance))))

colnames(plotdata) <- c('Family','Order','N','Island')

plotdata$Family <- factor(plotdata$Family,
                         levels = ara.abundance$Família)

ggplot(data = plotdata, aes(x = Family, y = N, group = Island, fill = Island))+
  geom_bar(stat = 'identity', position = position_dodge()) + 
  theme(axis.text.x = element_text(angle = 50, vjust = 0.9, hjust=1))+
  ggtitle("Abundance of orders")
ggsave('output/insect_order_abundance_oct2022.png', width = 9, height = 7)

save.image('role_af.RData')
```

Thinking of elevation and island-like system in southern AF:

```{r}
library(sf)
library(tidyverse)
library(raster)
study.area <- c(-60.94043,-33.21999,-33.98999,-1.12)
study.crs <- "+proj=longlat +datum=WGS84 +no_defs"

# Creating AF Shapefile
af.shapefile <- st_read('data/spatial_layers/official_teow_samer/official_teow_samer.shp')
st_crs(af.shapefile) <- study.crs
eco.names <- c("Alto Paraná Atlantic Forests","Araucaria Moist Forests",
               "Bahia Coastal Forests","Bahia Interior Forests","Caatinga Enclaves Moist Forests",
               "Pernambuco Coastal Forests","Pernambuco Interior Forests","Serra Do Mar Coastal Forests",
               "Atlantic Dry Forests")

af.shapefile <- af.shapefile %>% filter(ECO_NAME %in% eco.names)

write_sf(af.shapefile,'data/spatial_layers/af.shapefile.ecorr/af.shapefile.ecorr.shp')

elevation <- raster('data/spatial_layers/wc2.1_30s_elev/wc2.1_30s_elev.tif')

# EXTRACT ELEVATION PER ECORREGION (MEAN, SD, RANGE) to visualize possible community differences

# LOOK FOR A VEGETATION

```

Collapsing insect spreadsheet for SISGEN

```{r}

insects <- read.csv('data/role_insects_triage_oct2022.csv')

tombo <- paste0(insects$Código.da.coleção, insects$Tombo.MHNBA)
insects <- data.frame(insects,tombo)

sisgen.table <- insects %>% group_by(Ordem) %>%
  summarise(city = unique(Município))

tombo <- c()
for (i in 1:nrow(sisgen.table)) {
  tombo <- rbind(tombo,paste(insects$tombo[which(insects$Ordem==as.character(sisgen.table[i,1]) & insects$Município==as.character(sisgen.table[i,2]))],collapse = ', '))
}
sisgen.table <- data.frame(sisgen.table, tombo = tombo)
write.table(sisgen.table,'data/sisgen.table.oct.2022.txt',row.names = F, col.names = T, quote = F, sep='\t')
```

## Dec 22, 2022

Wrangle presence data list per island.
This data came from personal lists. In the future, it will be complemented through sound recording.

```{r}

```

Create data set with species and their respective phylogenetic (family and genus) and trait data.

First define a list of the metacommunity. Probably based on wikiaves/ebird/birdlife and radius around local community.

Load that list here and derive family, traits and abundance from different datasets:
- Family: Bird 2020
- Body size: ATLANTIC BIRDS TRAIT / HBW / My own data
- Wing length / Tarsus Length: AVONET
- Forest Sensitivity: Stotz - Personal knowledge
- Diet: Elton Traits / Bird 2020
- Trophic level: AVONET
- Abundance: ebird/birdlife record numbers? Download all records from one of these databases in each locality, and in the metacommunity, and count reative proportion of records?

Some of these datasets will not have all species. Also, some knowledge will need to be added manually.

```{r}

```

Wrangle all that data here into one big master spreadsheet for the preliminary analyses
